\section{Versioning}
\label{sec:version}

Because one of the goals of \texttt{cleverhans} is to provide a basis for
reproducible benchmarks, it is important that the version numbers provide useful
information. The library uses semantic
versioning,\footnote{\url{http://semver.org/}} meaning that version numbers take
the form of MAJOR.MINOR.PATCH.

The PATCH number increments whenever backwards-compatible bug fixes are made.
For the purpose of this library, a bug is not considered backwards-compatible if
it changes the results of a benchmark test. The MINOR number increments whenever
new features are added in a backwards-compatible manner. The MAJOR number
increments whenever an interface changes.

As of this writing, no bug affecting the accuracy of a performance number used
for a benchmark has ever been discovered. If one is discovered in the future,
fixing this bug would cause the MAJOR number to increment, because it is
considered a change in the interface mapping from the specification of a
benchmark to the reported performance. Release notes accompanying each revision
will indicate whether an increment to the MAJOR number invalidates earlier
benchmark results or not.

\section{Version notes}

Version 1.0.0 contains the following new features and improvements since v0.1:
\begin{itemize}
\item  Added {\tt jsma} , the saliency map attack
\item Improved the MNIST model in the tutorial, for greater speed and accuracy
\end{itemize}

The major version number has incremented due to bug fixes that affect the reproducibility of benchmarks:
\begin{itemize}
\item Fixed a bug in {\tt tf\_model\_loss} that reduced the effectiveness of both model training and adversarial example construction.
\item Fixed a bug in {\tt tf\_model\_eval} that could result in overestimating the accuracy.
\end{itemize}
For this reason, any benchmarks collected using v0.1 should be replaced using benchmarks
collected using v1.0.0.
